Identification of Direct Cherenkov Pixels using Boosted Decision Trees

### 2016-12-07 report/updated.tex
Final Thesis Update 07/12/16

\documentclass[11pt]{article}
\usepackage{graphicx}
\graphicspath{ {graphs/} }
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1.0in}
\usepackage{gensymb}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{pgfplotstable, booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{afterpage}
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}
\onehalfspacing

@@

        \today

@@

The basis of this thesis work can be divided into two halves. The first half is the simulation of Cosmic Ray HESS camera images, and analysis work based on these images. The second half is a Monte Carlo study simulating air shower intensities, based entirely on function fitted from the HESS camera images. It is important to note that the simulation of Cosmic Ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Telarray software \cite{Bernlohr08}. I claim no credit for the complex simulations that these packages have enabled me to perform.

Additionally, a significant portion of this work relies on Supervised machine learning that was performed using the SciKit learn package \cite{scikit-learn}. Although I wrote the relevant Python scripts to facilitate data categorisation and algorithm training, the package acts as a black box to convert training data into a functioning Boosted Decision Tree. I would like to make clear that I am indebted to those who produced this package, without whom this analysis could not have been performed.

@@

All such telescope arrays currently rely on Hillas Analysis to fully reconstruct the events, including the  charge Z of the Cosmic Ray. Hillas Analysis relies on extracted parameters from each of the camera images, but heavy atmospheric blurring of these images means that charge resolution is very poor. For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}. The Cosmic Rays imaged by these telescopes have energies in TeV scale, and at present, no study of the relative abundance of different cosmic ray elemental abundances exists at these energies. If the telescope arrays could be used to spectroscopically analyse the Cosmic Rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy. However, current charge resolution from Hillas Analysis is not small enough to undertake such a study. The principal goal of this thesis is to enable spectroscopic analysis with Cherenkov Telescope arrays, by improving the charge resolution of reconstructed events.

@@

The refractive index as a function of height is shown in as seen in Figure \ref{fig:lpd}, using standard values listed in the appendix. Because the refractive index of air increases very quickly as the height decreases, the Cherenkov Angle $\theta_{C}$ will also increase rapidly with decreasing height. Thus, although the displacement $(h - altitude_{array})$ decreases with height, the radius on the ground will nonetheless increase as height decreases. Consequently the upper atmosphere emission contributes to the inner LPD, while the lower atmosphere emission contributes to the outer LPD. As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.

@@

Above threshold, Cherenkov Emission is determined by the Frank Tamm formula \cite{ppreview}.  Under the assumption of constant magnetic permittivity and a zenith angle of $90\degree$, and with  the vertical distance travelled in meters $\Delta_{h}$ and the emission energy range in eV $\Delta_{E}$, we can find an approximate Cherenkov Emission formula.
\[ \frac{d^{2}N_{photons}}{dEdh} = \frac{\alpha Z^{2}}{\hbar c} \sin^{2} \theta_{c}(E) \approx 370 Z^{2} \sin^{2} \theta_{c}(E)\, cm^{-1}eV^{-1} \]

@@

If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LPD shown in Figure \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$ . Thus the amplitude of the LPD is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission. This proportionality is the basis for charge reconstruction in the LPD method.

@@

The refractive index at a series of heights, based on data from the HESS site, is shown \ref{fig:lpd}. Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted. Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation. This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LPD.

@@

The full simulation of air showers was performed using CORSIKA with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. This is included in the Appendix. In total, 5000 training events and a further 10000 testing events were simulated. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a flux spectrum $\phi(E) \propto E^{-2.7}$. For each set of simulated event, 4 unique random number seeds were used to generate the shower. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis. Due to hardware differences between CT5 and the original HESS 1 telescopes, we analyse HESS1 and HESS2 images separately.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{hess1statsbigtestdata}
\caption{The DC signal in the shower-free pixel is shown in the top left, with a broad gaussian distribution with the tail of the night-sky background extending up to appproximately 5000. Events below this are unlikely to be identified correctly because the DEC light is too faint. In the top right- the distribution of the dataset is shown, once all the non-$Q_{DC}$ cuts have been applied. In the bottom left, the BDT score distribution is shown before any cuts. On the bottom right, we see the same distribution after both signal and BDT score cuts are applied. All green events are ones in which the DC pixel has been correctly identified, while red events are ones that have been incorrectly identified.}
\label{fig:cutdistribution}
\end{center}
\end{figure}

@@

Instead of rejecting DC pixels which do not meet out $DC_{count}$ and $P_{signal}$ cuts, we can separately measure their deviation from the LPD. In this way, we can include the information from these DC pixels in later analysis, while accounting for the larger uncertainty in their LPD measurements. For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\frac{\sigma_{rejected}}{DC_{rgr}}=0.15$. It would be interesting to incorporate the information from these pixels into reconstruction, but doing so would remove our ability to constrain the core. Further study could attempt to use the rejected pixels, though the performance of the regressor on images without DC light would first need to be thoroughly tested to account for the possibility that rejected pixels belong top images without DC light. Because the BDT regressor functions as a Black Box, it is difficult to know how it is using the information from camera images to calculate $DC_{rgr}$. To ensure the validity of our Monte Carlo simulation, we will omit the rejected pixels as part of this analysis.

@@

\section{Monte Carlo Simulation}
Having obtained a parameterisation for both the full and DC LPD, as well as the associated error in the case of a HESS-type array, the Charge reconstruction Technique can be applied to a simpified Monte Carlo simulation of the HESS array, developed as part of this analysis. Conducting a Monte Carlo simulation using the Gaussian-smeared LPD, we can measure the effectiveness of the LPD-reconstruction technique. The simulated Cosmic Rays must be high-multiplicity, and have a realistic distribution of energy and interaction height values.

@@

\begin{figure}
\begin{center}
\includegraphics[height=0.9\textheight]{generalheight}
\caption{The integrated interaction lengths increases as height decreases. Thus the decay probability follows a exponentially increasing distribution. The mean first interaction height for all events is roughly 40km above sea level.}
\label{fig:generalheight}
\end{center}
\end{figure}

@@

Thus, we can simply calculate $x_{0}$ as the expectation value of interaction length. This parameter is free-floating, and can only be determined through experimental study of Cosmic Rays. Experimental results indicate an approximate cross section of $\sigma_{Fe-air} = 2000mb$ and a corresponding thus $x_{0} \approx 12 g cm^{-2}$ \cite{Montanus2013}.

@@

Another parameter that could be exponetially the optical depth to the surface, $\tau$. The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption. The major of Rayleigh scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height. For a given emitted intensity $I_{0}$ we find that the corresponding I received on the ground decays exponentially with optical depth, so that $\frac{I}{I_{0}}=e^{-\tau}$ with $\tau=\int_{0}^{l}ds$. However, the CORSIKA parameterisation has already accounted for any influence of atmospheric absorption. It is likely that this, in part, contributed to the value of $\sigma_{DCrgr}$.

@@

In combination, we consequently have a total of 1000 minimisations. Having run the minimisation algorithm, we thus acheive a full-shower LPD reconstruction, and obtain a measurement of the core energy and starting position. The resulting fraction error in energy distribution is shown below in Figure \ref{fig:rawepn}. Under the assumption of a gaussian distribution, we can calculate the mean fractional deviation as half of the distance between the 16th and 84th centiles of data. We sort each fractional deviation, and expect that 68\% of events will lie between these values. Using this method, it is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered. We find that the position is also reconstructed, with an accuracy of . Having now reconstructed the value of the energy with reasonable accuracy, we can make use of this value when attempting to reconstruct the DC LPD.

@@

As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core. The results of a binning of this distribution are shown in Figure \ref{fig:rawposition}. Because we consider absolute distance, this value can never be negative. Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation. It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} = 9.1m$ and $\sigma_{core} 17.0m$ respectively. Considered together, we conclude that most high-multiplicity reconstructed core positions thus lie less than 15m from the true position. This is reasonably good, especially in comparison to the Hillas Reconstruction, where a core position resolution of $\sigma_{core} \approx 20m$ is more typical.

@@

Having taken into account our various variable uncertainties, we can also consider our most important variable. In Figure \ref{fig:rawZ} the reconstructed charge number is binned in integers, illustrating the element that each reconstructed event would be assigned to. As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value. The distributions are broadly symmetric, and have a charge resolution of $\sigma_{Z} = 1.1$ and $\sigma_{Z} = 2.2$ for five and four telescope events respectively. Unsurprisingly, the charge resolution is better for five-telescope events, but both cases represent a significant improvement over the existing charge resolution obtained through Hillas analysis. With the reasonably high event rate, we could certainly expect to see such a peak in the existing HESS data, and the uncertainty may be small enough to enable spectroscopic analysis. Obtaining such a peak is a vindication of the LPD method, and demonstrates its superior performance for event reconstruction. However, the value of $\sigma_{Z}$ for 4-telescope events is still large. It is also clear in Figure \ref{fig:rawZ} that the distribution is somewhat truncated by the imposed minimisation reconstruction range of 16-36.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Likelihood}
\caption{The BDT score distribution is shown for the Monte Carlo test data. Events are colour-coded by how well the Charge number was reconstructed. We see that the majority of bad red events have a lower BDT score in the 4-tel graph. In each graph, the think black line indicates the eventual cut made to the data.}
\label{fig:reconBDTdistribution}
\end{center}
\end{figure}

Having obtained a BDT score variables $P_{4tel}$ and $P_{5tel}$, we can then optimise cuts on this variable. The two BDTs will be optimised independently. Our aim is to reduce the value of $\sigma_{Z}$ to provide a narrower reconstructed peak. This should enable more effective spectroscopic analysis. At the same time, we wish to maintain as high a pass rate as possible, to reduce the expected random Poissonian Error in the dataset. We know that the Poissonian Error of a distribution scales with $\frac{1}{\sqrt{N}}$. Ultimately we expect to obtain a spectrum of overlapping Gaussians corresponding to each element, and fit for the relative height of each Gaussian. To balance the competing priorities of large N and small $\sigma_{Z}$ which will enable the Gaussian peaks to be resolved, we can define a new scaled variable $\mathbf{\tilde{\sigma_{Z}}} = \frac{\sigma_{Z}}{\sqrt{(f)}}$. Here, instead of N, we are scaling with the passing fraction of events $f = \frac{N_{passing}}{N_{total}}$. The quantity $\mathbf{\tilde{\sigma_{Z}}}$ is then found for a range of BDT cut values, and the minimum found. The values of $\sigma_{Z}$ and $\mathbf{\tilde{\sigma_{Z}}}$ are shown in Figure \ref{fig:Zcuts}. Ultimately, a cut of $P_{4tel} > 0.15$ and $P_{5tel} > 0.22$ was chosen, corresponding to $\sigma_{Z}=0.88$ and $\sigma_{Z}=1.04$ respectively. The respective passing fraction was 0.92 and 0.53. The improvement for 5 telescope events is minor, but for 4 telescope events there is a significant reduction in charge resolution.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Zcuts}
\caption{The BDT score distribution is shown for the Monte Carlo test data. Events are colour-coded by how well the Charge number was reconstructed. We see that the majority of bad red events have a lower BDT score in the 4-tel graph. In each graph, the think black line indicates the eventual cut made to the data.}
\label{fig:Zcuts}
\end{center}
\end{figure}

@@

This makes sense, as cores close to a telescope are likely to produce negligible DC light in that telescope. However, once the $P_{4tel}$ cut is applied, the majority of events lying outside the square of small telescopes are removed. Also, interestingly, most events lying near one of the smaller telescopes are removed, giving each telescope a noticeable halo containing few or no events. This suggests that, if an event lies close to one telescope, the distance to the opposite diagonal telescope is likely to be too large to produce a DC signal. Thus, we would instead expect a 3-tel event. We know that the first interaction height is reconstructed extremely poorly, and thus the exact $r_{max}$ values for these LPDs is uncertain. It is likely that, given this, the height is being misreconstructed to allow the LPD to extend fare enough to trigger the most distant telescope.

@@

As might be expected, the loose $P_{5tel}$ cuts produce little noticeable difference to the distribution. However, there is a clear curtailing of the lower Energy events after the $P_{4tel}$ cut has been applied. This is as might be expected, because events that are not saturated in Energy are unlikely to be reconstructed well. Ultimately, the post cut distributions of 4-tel events appears similar to the 5-tel distribution, albeit with a greater overall frequency. Both are lie closer to the simulated distribution once cuts have been applied. In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes even when compared to the 5-tel rather than simulated distribution. The results broadly vindicate our decision to apply an Energy Cut on reconstructed events that was implemented to remove protons. Were the lower Energy Iron events to have been included in our simulations, we would have needed to remove them through the BDT method because they are unlikely to be reconstructed well. Having applied the BDT cuts, we see that the 5-tel distribution broadly follows the simulated distribution with a relative height of 0.6\%, while the 4-tel events follow the simulated distribution with a relative height of 1.8\%.

@@

\subsection{Actual Data}
The obvious next step to take as part of this analysis would be to apply the reconstruction Method to real HESS data. We would hope to obtain a distribution similar to that in Figure \ref{fig:Z}, to which we could fit Gaussians centered on each integer value of Charge. In this way, we could calculate the relative abundance of the different Heavy Cosmic rays. Comparing the width of these Gaussians would confirm whether or not our reconstruction method was optimistic in our various assumptions for error. Additionally, on the basis of the calculated expectation rate for Iron Events we could compare to see if this agrees
with the data. An excessive experimental count rate would likely indicate that additional sources of background, such as protons, are passing the various cuts. To compensate for this, additional cuts would need to be designed and applied, which would likely lead to reductions in expected Iron acceptance rate.

In the event that the experimental method proves successful, it should be possible to use the exact position of the iron peak as a method of calibration for atmospheric absorption. An underestimate of the CORSIKA absorption used in training would lead to an iron peak that was shifted to a charge number lower than 26, due to a lower than unexpected photon count. Similarly, the reverse would apply if the modelled atmospheric absorption was an overestimate. As these is much associated uncertainty in the atmospheric properties, this would be a useful measurement to perform.

@@

Our only viable alternative is to develop a technique for measuring $True_{DC}$ without fully simulating the entire LPD. Fortunately, the BDT regressor was able to  do exactly this. The fractional standard deviation was reduced of the BDT was just $\frac{\sigma_{rgr}}{DC_{rgr}} = 0.14$ for a sample of mixed interaction heights, as opposed to $\frac{\sigma_{TrueDC}}{True_{DC}} = 0.48$ when the actual DC light was measured. With 4 or 5 LPD measurements, this BDT regressor was capable of giving an amplitude proportional to $Z^{2}$ with sufficient precision to enable reconstruction. The regressor was able to the necessary precision by correlating a number of image and pixel variables such as the Image Amplitude and Aspect Ratio. The BDT must indirectly be inferring the charge number, but by providing this information in the form of an LPD rather than a simple number, we are able to reconstruct the charge using all available information. It would be interesting to explore the possibility of a BDT that would directly calculate the charge number of a Cosmic Ray based on a given Image, but this was not done as part of this analysis.

>>>>

\documentclass[11pt]{article}
\usepackage{graphicx}
\graphicspath{ {graphs/} }
\usepackage{geometry}
\geometry{a4paper, portrait, margin=1.0in}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{pgfplotstable, booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{afterpage}
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}
\onehalfspacing

@@

        \day4
        \month 7
        \year 2016
        \today

@@

The basis of this thesis work can be divided into two halves. The first half is the simulation of Cosmic Ray HESS camera images, and analysis work based on these images. The second half is a Monte Carlo study simulating air shower intensities, with event reconstruction based on function-fitting to these intensities. It is important to note that the simulation of Cosmic Ray air showers for the first part of my thesis was performed using the CORSIKA software \cite{Heck98}, and the resultant HESS camera images were produced using the Sim\textunderscore Telarray software \cite{Bernlohr08}. I claim no credit for the complex simulations that these packages have enabled me to perform.

Additionally, a significant portion of this work relies on supervised machine learning that was performed using the SciKit learn package \cite{scikit-learn}. Although I wrote the relevant Python scripts to facilitate data categorisation and algorithm training, the package acts as a black box to convert training data into a functioning Boosted Decision Tree. I would like to make clear that I am indebted to those who produced this package, without whom this analysis could not have been performed.

@@

All such telescope arrays currently rely on Hillas Analysis to fully reconstruct the events, including the  charge Z of the Cosmic Ray. Hillas Analysis relies on extracted parameters from each of the camera images, but heavy atmospheric blurring of these images means that charge resolution is very poor. For Iron Nucleus events, we would expect to reconstruct \[Z \approx 26 \pm 5 \] with a core position resolution of roughly $d \approx 20 m $ \cite{hess07}. The Cosmic Rays imaged by these telescopes have energies in TeV scale, and at present, no study of the relative cosmic ray elemental abundances exists at these energies. If the telescope arrays could be used to spectroscopically analyse the Cosmic Rays, it could provide important clues regarding the mechanism of Cosmic Ray formation and propagation in the galaxy. However, current charge resolution from Hillas Analysis is not small enough to undertake such a study. The principal goal of this thesis is to enable spectroscopic analysis with Cherenkov Telescope arrays, by improving the charge resolution of reconstructed events.

@@

The refractive index as a function of height is shown in Figure \ref{fig:lpd}, using standard values listed in the appendix. Because the refractive index of air increases very quickly as the height decreases, the Cherenkov Angle $\theta_{C}$ will also increase rapidly with decreasing height. Thus, although the displacement $(h - altitude_{array})$ decreases with height, the radius on the ground will nonetheless increase as height decreases. Consequently the upper atmosphere emission contributes to the inner LPD, while the lower atmosphere emission contributes to the outer LPD. As the cosmic ray travels down through the atmosphere, Cherenkov Emission continuously illuminates new areas on the ground that were previously unlit, without re-illuminating inner regions.

@@

Above threshold, Cherenkov Emission is determined by the Frank Tamm formula \cite{ppreview}.  Under the assumption of constant magnetic permittivity and a zenith angle of $90^{\circ}$, and with  the vertical distance travelled in meters $\Delta_{h}$ and the emission energy range in eV $\Delta_{E}$, we can find an approximate Cherenkov Emission formula.
\[ \frac{d^{2}N_{photons}}{dEdh} = \frac{\alpha Z^{2}}{\hbar c} \sin^{2} \theta_{c}(E) \approx 370 Z^{2} \sin^{2} \theta_{c}(E)\, cm^{-1}eV^{-1} \]

@@

If we divide the number of emitted photons by the area of the annulus between the ring radii at $h$ and $h - \Delta_{h}$, we retrieve the LPD shown in Figure \ref{fig:lpd}, which varies with $ \rho_{DC}  = f(r) \times Z^{2}$. Thus the amplitude of the LPD is proportional to the square of the Cosmic Ray charge, enabling us to reconstruct this number from the DC emission. This proportionality is the basis for charge reconstruction in the LPD method.

@@

The refractive index at a series of heights, based on data from the HESS site, is also shown \ref{fig:lpd}. Exponentials are fitted between points to provide interpolation, and a comparison can be made to a linear interpolation that is also plotted. Despite the exponential interpolation, discontinuities in the second derivative of the refractive index prevent the LPD from being smooth in the simulation. This is unimportant, because in reality the variation due to atmospheric conditions and random noise will smear out any discontinuities in the LPD.

@@

The full simulation of air showers was performed using CORSIKA with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. This is included in the Appendix. In total, 5000 training events and a further 10000 testing events were simulated. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a flux spectrum $\phi(E) \propto E^{-2.7}$. For each set of simulated event, 4 unique random number seeds were used to generate the shower. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0^{\circ} < \theta < 2 ^{\circ}$, while the simulated azimuth angle ranges from $-2^{\circ} < \phi < 2 ^{\circ}$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis. Due to hardware differences between CT5 and the original HESS 1 telescopes, we analyse HESS1 and HESS2 images separately.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{hess1statsbigtestdata}
\caption{The DC signal in the shower-free pixel is shown in the top right, following an exponential decay. Events below roughly 200 are unlikely to be identified correctly because the DC light is too faint to be seen against the background. In the top left, the BDT score distribution is shown before any cuts. In the lower left, we see the same distribution after both signal and BDT score cuts are applied. For comparison, the lower right graph shows the alternative distribution of $Q_{DC}$-reconstructed events. All green events are ones in which the DC pixel has been correctly identified, while grey events are ones that have been incorrectly identified.}
\label{fig:cutdistribution}
\end{center}
\end{figure}

@@

Instead of rejecting DC pixels which do not meet out $DC_{count}$ and $P_{signal}$ cuts, we can separately measure their deviation from the LPD. In this way, we can include the information from these DC pixels in later analysis, while accounting for the larger uncertainty in their LPD measurements. For images which do pass only the multiplicity cuts, but not the $P_{signal}$ or $DC_{count}$ cuts, we find that the regressor error is $\frac{\sigma_{rejected}}{DC_{rgr}}=0.15$. It would be interesting to incorporate the information from these pixels into reconstruction, but doing so would remove our ability to constrain the core. Further study could attempt to use the rejected pixels, though the performance of the regressor on images without DC light would first need to be thoroughly tested to account for the possibility that rejected pixels belong to images without DC light. Because the BDT regressor functions as a Black Box, it is difficult to know how it is using the information from camera images to calculate $DC_{rgr}$. To ensure the validity of our Monte Carlo simulation, we will omit the rejected pixels as part of this analysis.

@@

\section{Monte Carlo Simulation}
Having obtained a parameterisation for both the full and DC LPD, as well as the associated error in the case of a HESS-type array, the charge reconstruction technique can be applied to a simplified Monte Carlo simulation of the HESS array, developed as part of this analysis. Conducting a Monte Carlo simulation using the Gaussian-smeared LPD, we can measure the effectiveness of the LPD-reconstruction technique. The simulated Cosmic Rays must be high-multiplicity, and have a realistic distribution of energy and interaction height values.

@@

\begin{figure}
\begin{center}
\includegraphics[height=0.9\textheight]{generalheight}
\caption{Above, the integrated interaction lengths increases as height decreases. Thus the decay probability follows a exponentially increasing distribution. In the centre, the survival and decay fractions are illustrated as a function of height. The median occurs around 40km, where the two lines intersect. Below, the fraction of interacting particles in each height band is shown in a histogram. The mean first interaction height for all events is roughly 40km above sea level.}
\label{fig:generalheight}
\end{center}
\end{figure}

@@

Thus, we can simply calculate $x_{0}$ as the expectation value of interaction length. This parameter is free-floating, and can only be determined through experimental study of Cosmic Rays. Experimental results indicate an approximate cross section of $\sigma_{Fe-air} = 2000mb$ and thus a corresponding value of $x_{0} \approx 12 g cm^{-2}$ \cite{Montanus2013}.

@@

Another parameter that could be modelled is $\tau$, the optical depth to the surface. The Cherenkov Light, mostly emitted in the visible blue part of the EM spectrum, experiences relatively little atmospheric absorption. The major component of Rayleigh-scattering-based atmospheric absorption occurs in the lower part of the troposphere, and thus the atmospheric absorption is almost independent of emission up to first interaction height. For a given emitted intensity $I_{0}$ we find that the corresponding I received on the ground decays exponentially with optical depth, so that $\frac{I}{I_{0}}=e^{-\tau}$ with $\tau=\int_{0}^{l}ds$. However, the CORSIKA parameterisation has already accounted for any influence of atmospheric absorption. It is likely that this, in part, contributed to the value of $\sigma_{DCrgr}$.

@@

In combination, we consequently have a total of 1000 minimisations. Having run the minimisation algorithm, we thus acheive a full-shower LPD reconstruction, and obtain a measurement of the core energy and starting position. The resulting fraction error in energy distribution is shown below in Figure \ref{fig:rawepn}. Under the assumption of a gaussian distribution, we can calculate the mean fractional deviation as half of the distance between the 16th and 84th centiles of data. We sort each fractional deviation, and expect that 68\% of events will lie between these values. Using this method, it is clear that the energy reconstruction is fairly good, with a fractional standard deviation of roughly 0.10 when both four and five telescope events are considered. Having now reconstructed the value of the energy with reasonable accuracy, we can make use of this value when attempting to reconstruct the DC LPD.

@@

As an alternative metric for assessing reconstruction accuracy, we can calculate the absolute distance from the reconstructed core to the true core. The results of a binning of this distribution are shown in Figure \ref{fig:rawposition}. Because we consider absolute distance, this value can never be negative. Thus, we calculate a one-sided distribution standard deviation, and consider the value of an event in the 68th centile to be equal to the standard deviation. It is found that, for both four and five telescope events, the core reconstruction is approximately $\sigma_{core} = 9.1m$ and $\sigma_{core}=17.0m$ respectively. Considered together, we conclude that most high-multiplicity reconstructed core positions thus lie less than 15m from the true position. This is reasonably good, especially in comparison to the Hillas Reconstruction, where a core position resolution of $\sigma_{core} \approx 20m$ is more typical.

@@

Having taken into account our various variable uncertainties, we can also consider our most important variable. In Figure \ref{fig:rawZ} the reconstructed charge number is binned, illustrating the expected experimental results. As we would hope, there is a very clear peak centered on Z=26, and the median charge value lies very close to this value. The distributions are broadly symmetric, and have a charge resolution of $\sigma_{Z} = 1.1$ and $\sigma_{Z} = 2.2$ for five and four telescope events respectively. Unsurprisingly, the charge resolution is better for five-telescope events, but both cases represent a significant improvement over the existing charge resolution obtained through Hillas analysis. With the reasonably high event rate, we could certainly expect to see such a peak in the existing HESS data, and the uncertainty may be small enough to enable spectroscopic analysis. Obtaining such a peak is a vindication of the LPD method, and demonstrates its superior performance for event reconstruction. However, the value of $\sigma_{Z}$ for 4-telescope events is still large. It is also clear in Figure \ref{fig:rawZ} that the distribution is somewhat truncated by the imposed minimisation reconstruction range of 16-36.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Likelihood}
\caption{The BDT score distribution is shown for the Monte Carlo test data. Events are colour-coded by how well the Charge number was reconstructed. We see that the majority of bad red events have a lower BDT score in the 4-tel graph. In each graph, the thick black line indicates the eventual cut made to the data.}
\label{fig:reconBDTdistribution}
\end{center}
\end{figure}

Having obtained a BDT score variables $P_{4tel}$ and $P_{5tel}$, we can then optimise cuts on this variable. The two BDTs will be optimised independently. Our aim is to reduce the value of $\sigma_{Z}$ to provide a narrower reconstructed peak. This should enable more effective spectroscopic analysis. At the same time, we wish to maintain as high a pass rate as possible, to reduce the expected random Poissonian Error in the dataset. We know that the Poissonian Error of a distribution scales with $\frac{1}{\sqrt{N}}$. Ultimately we expect to obtain a spectrum of overlapping Gaussians corresponding to each element, and fit for the relative height of each Gaussian. To balance the competing priorities of large N and small $\sigma_{Z}$ which will enable the Gaussian peaks to be resolved, we can define a new scaled variable $\mathbf{\tilde{\sigma_{Z}}} = \frac{\sigma_{Z}}{\sqrt{(f)}}$. Here, instead of N, we are scaling with the passing fraction of events $f = \frac{N_{passing}}{N_{total}}$. The quantity $\mathbf{\tilde{\sigma_{Z}}}$ is then found for a range of BDT cut values, and the minimum found. The values of $\sigma_{Z}$ and $\mathbf{\tilde{\sigma_{Z}}}$ are shown in Figure \ref{fig:Zcuts}. Ultimately, a cut of $P_{4tel} > 0.21$ and $P_{5tel} > 0.15$ was chosen, corresponding to $\sigma_{Z}=0.88$ and $\sigma_{Z}=1.04$ respectively. The respective passing fraction was 0.92 and 0.53. The improvement for 5 telescope events is minor, but for 4 telescope events there is a significant reduction in charge resolution.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{Zcuts}
\caption{Above, the raw values for $\sigma_{Z}$ are shown as a function of the BDT cuts for 4-tel and 5-tel events. Below, the scaled values of $\mathbf{\tilde{\sigma_{Z}}}$ are shown. For 4-tel events, there is a clear minimum for $P_{4tel} > 0.21$, while for 5-tel events, there is a broader minimum at $P_{5tel} > 0.15$.}
\label{fig:Zcuts}
\end{center}
\end{figure}

@@

This makes sense, as cores close to a telescope are likely to produce negligible DC light in that telescope. However, once the $P_{4tel}$ cut is applied, the majority of events lying outside the square of small telescopes are removed. Also, interestingly, most events lying near one of the smaller telescopes are removed, giving each telescope a noticeable halo containing few or no events. This suggests that, if an event lies close to one telescope, the distance to the opposite diagonal telescope is likely to be too large to produce a DC signal. Thus, we would instead expect a 3-tel event. We know that the first interaction height is reconstructed extremely poorly, and thus the exact $r_{max}$ values for these LPDs is uncertain. It is likely that, given this, the height is being misreconstructed to allow the LPD to extend far enough to trigger the most distant telescope.

@@

As might be expected, the loose $P_{5tel}$ cuts produce little noticeable difference to the distribution. However, there is a clear curtailing of the lower Energy events after the $P_{4tel}$ cut has been applied. This is as might be expected, because events that are not saturated in Energy are unlikely to be reconstructed well. Ultimately, the post cut distributions of 4-tel events appears similar to the 5-tel distribution, albeit with a greater overall frequency. Both lie closer to the simulated distribution once cuts have been applied. In contrast, the pre-cuts 4-tel events had a noticeable broader distribution extending further into the very low and very high energy regimes even when compared to the 5-tel rather than simulated distribution. The results broadly vindicate our decision to apply an Energy Cut on reconstructed events that was implemented to remove protons. Were the lower Energy Iron events to have been included in our simulations, we would have needed to remove them through the BDT method because they are unlikely to be reconstructed well. Having applied the BDT cuts, we see that the 5-tel distribution broadly follows the simulated distribution with a relative height of 0.6\%, while the 4-tel events follow the simulated distribution with a relative height of 1.8\%.

@@

\subsection{Actual Data}
The obvious next step to take as part of this analysis would be to apply the reconstruction method to real HESS data. We would hope to obtain a distribution similar to that in Figure \ref{fig:Z}, to which we could fit Gaussians centered on each integer value of Charge. In this way, we could calculate the relative abundance of the different Heavy Cosmic rays. Comparing the width of these Gaussians would confirm whether or not our reconstruction method was optimistic in our various assumptions for error. Additionally, on the basis of the calculated expectation rate for Iron Events we could compare to see if this agrees
with the data. An excessive experimental count rate would likely indicate that additional sources of background, such as protons, are passing the various cuts. To compensate for this, additional cuts would need to be designed and applied, which would likely lead to reductions in expected Iron acceptance rate.

In the event that the experimental method proves successful, it should be possible to use the exact position of the iron peak as a method of calibration for atmospheric absorption. An underestimate of the CORSIKA absorption used in training would lead to an iron peak that was shifted to a charge number lower than 26, due to a lower than unexpected photon count. Similarly, the reverse would apply if the modelled atmospheric absorption was an overestimate. As there is much associated uncertainty in the atmospheric properties, this would be a useful measurement to perform.

@@

Our only viable alternative is to develop a technique for measuring $True_{DC}$ without fully simulating the entire LPD. Fortunately, the BDT regressor was able to  do exactly this. The fractional standard deviation was reduced of the BDT was just $\frac{\sigma_{rgr}}{DC_{rgr}} = 0.14$ for a sample of mixed interaction heights, as opposed to $\frac{\sigma_{TrueDC}}{True_{DC}} = 0.48$ when the actual DC light was measured. With 4 or 5 LPD measurements, this BDT regressor was capable of giving an amplitude proportional to $Z^{2}$ with sufficient precision to enable reconstruction. The regressor was able to the necessary precision by correlating a number of image and pixel variables such as the Image Amplitude and Aspect Ratio. The BDT must indirectly be inferring the charge number, but by providing this information in the form of an LPD rather than a simple number, we are able to reconstruct the charge using all available information. It would be interesting to explore the possibility of a BDT that would directly calculate the charge number of a Cosmic Ray based on a given image, but this was not done as part of this analysis.
